Download data

### 2024-02-20 scripts/subsetDataforCrews.Rmd
mapping

```{r jitter the AIM data, eval = F}
set.seed(125)
occ_p <- '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/combined_records'
occurrences <- lapply(
  file.path(occ_p, list.files(occ_p, pattern = 'shp$')), st_read, quiet = T) |>
  bind_rows() %>% 
  filter(Occurrence == 1) %>% 
  select(taxon, date, PtType)
occ_aim <- filter(occurrences, PtType == 'AIM Presence') %>% 
  st_jitter(amount = 250)
occurrences <- bind_rows(
  filter(occurrences, PtType != 'AIM Presence'), 
  occ_aim) %>% 
  mutate(
    PtType = if_else(PtType == 'AIM Presence', 'jittered', 'exact'),
    date = str_extract(date, '[0-9]{4}')
    ) %>% 
  rename(year = date, coord_status = PtType) %>% 
  arrange(taxon, year, coord_status)

st_write(occurrences, file.path(occ_p, 'jittered_occurrences.shp'), quiet = T)

@@

occ_p <- '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/combined_records'
occurrences <- st_read(file.path(occ_p, 'jittered_occurrences.shp'), quiet = T)

>>>>

```{r jitter the AIM data, eval = F}
set.seed(125)
occ_p <- '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/combined_records'
occurrences <- lapply(
  file.path(occ_p, list.files(occ_p, pattern = 'shp$')), st_read, quiet = T) |>
  bind_rows() %>% 
  filter(Occurrence == 1) %>% 
  select(taxon, date, PtType)
occ_aim <- filter(occurrences, PtType == 'AIM Presence') %>% 
  st_jitter(amount = 250)
occurrences <- bind_rows(
  filter(occurrences, PtType != 'AIM Presence'), 
  occ_aim) %>% 
  mutate(
    PtType = if_else(PtType == 'AIM Presence', 'jittered', 'exact'),
    date = as.numeric(str_extract(date, '[0-9]{4}'))
    ) %>% 
  rename(year = date, coord_status = PtType) %>% 
  arrange(taxon, year, coord_status)

st_write(occurrences, file.path(occ_p, 'jittered_occurrences.shp'), quiet = T, append = F)

@@

occ_p <- '/media/steppe/hdd/SDM_restorations/data/raw/occurrence/jittered_occurrences'
occurrences <- st_read(file.path(occ_p, 'jittered_occurrences.shp'), quiet = T)
